---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# Data Preprocessing

## Importing the dataset

#### Loading the dataset from a CSV file into a data frame structure.

```{r}
dataset = read.csv('C:/Users/DELL/Documents/SAIRUSHI/Machine Learning A_Z/Part 1 - Data Preprocessing/Data.csv')
head(dataset)
```

## Taking care of missing data

#### Handling missing values(if any) in the 'Age' and 'Salary' columns by replacing them with the mean of the column.

```{r}
dataset$Age = ifelse(is.na(dataset$Age),
                     ave(dataset$Age, FUN = function(x) mean(x, na.rm= TRUE)),dataset$Age)


dataset$Salary = ifelse(is.na(dataset$Salary),
                        ave(dataset$Salary, FUN = function(x) mean(x, na.rm = TRUE)),dataset$Salary)
```

## Encoding categorical data

#### Converting categorical variables into numeric values for machine learning models.

##### 'Country' is encoded as 1, 2, and 3 for France, Spain, and Germany, respectively.

```{r}
dataset$Country = factor(dataset$Country,
                         levels = c('France', 'Spain', 'Germany'),
                         labels = c(1, 2, 3))
```

#### 'Purchased' is encoded as 0 for No and 1 for Yes.

```{r}
dataset$Purchased = factor(dataset$Purchased,
                           levels = c('No', 'Yes'),
                           labels = c(0, 1))
```

#### Displaying the first few rows of the processed dataset

```{r}
head(dataset)
```
